Introduction to VERRSPM_Scenario

### 2021-04-20 sources/models/VEScenarios/tutorial_VEScenario.Rmd
Change models/VEScenario -> models/VEScenarios
- Add VEScenarios to the build components
- Formatting and spelling fixes throughout
- Still not completing runs through the tutorial

After creating this database when you run a sample visioneval model, a directory with all the scneario levels and required inputs will be created . see `runtime/VEScenario/scenario_inputs` for an example of the directory structure.
## Running VEScenario
After creating scenario manager file, you need to run VEScenario::NewScenarioSetInterior() function to 
create the scenario directories and populate with required inputs
                                                                                                        ```{r, echo=FALSE, message=FALSE, warning=FALSE}
VEScenario::NewScenarioSetInterior(ScenarioInputFolder=NULL,ScenarioManagerFile,ModelFolder,ScenarioBaselineInputFolder=NULL)
```                                                                                                     This function requires 4 inputs by user:

** ScenarioInputFolder — a file path identifying the location on the computer hard disk where the inputs for the scenarios will be located.
May be NULL, in which case ScenarioManagerFile is interpreted as the full path to the file, and ** ScenarioManagerFile is computed as basename(normalizePath(ScenarioInputFolder))
** ScenarioManagerFile — the file path of the CSV file described above, which is expected to be in the ScenarioInputFolder. 
** ModelFolder — The path to the folder containing the Base Model run_model.R  script that will run each of the constructed scenarios plus its other elements (inputs and defs sub-folders).
** ScenarioBaselineInputFolder — the location on the computer of the hard disk where the inputs used for the baseline scenarios are located.
May be NULL, in which case it is constructed as file.path(ModelFolder,”inputs”)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
VEScenario::BuildScenariosInterior(ScenarioInputFolder,ScenarioOutputFolder,ModelFolder)
```

@@

** ScenarioInputFolder — a file path identifying the location on the computer hard disk where the inputs for the scenarios will be located.
** ScenarioOutputFolder — file path identifying the location on the computer hard disk where the built scenarios will be located
** ModelFolder — The path to the folder containing the Base Model run_model.R  script that will run each of the constructed scenarios plus its other elements (inputs and defs sub-folders).

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
VEScneario_test <- openModel("VEScenario")
VEScneario_test $run()
```

>>>>

After creating this database when you run a sample visioneval model, a directory with all the scenario levels and required inputs will be created . see `runtime/models/VEScenario/scenario_inputs` for an example of the directory structure.

## Running VEScenario
After creating scenario manager file, you need to run VEScenario::NewScenarioSetInterior() function to 
create the scenario directories and populate with required inputs

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ScenarioManagerFile = "models/VEScenario/scenario_inputs/verspm_scenario_manager"
ModelFolder = "models/VERSPM"
VEScenario::NewScenarioSetInterior(ScenarioManagerFile,ModelFolder,ScenarioInputFolder=NULL,ScenarioBaselineInputFolder=NULL)
```

This function requires 4 inputs by user:

** ScenarioInputFolder — a file path identifying the location on the computer hard disk where the inputs for the scenarios will be located. In case ScenarioManagerFile is in this folder, it can be NULL.
** ScenarioManagerFile — the file path of the CSV file described above, which is expected ( but not required) to be in the ScenarioInputFolder. 
** ModelFolder — The path to the folder containing the Base Model run_model.R  script that will run each of the constructed scenarios plus its other elements (inputs and defs sub-folders).
** ScenarioBaselineInputFolder — the location on the computer of the hard disk where the inputs used for the baseline scenarios are located. In case the folder it inside the ModelFolder it can be NULL

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ScenarioInputFolder = "models/VEScenario/scenario_inputs"
ScenarioOutputFolder ="models/VEScenario/scenarios"
VEScenario::BuildScenariosInterior(ScenarioInputFolder,ScenarioOutputFolder,ModelFolder)
```

@@

** ScenarioInputFolder — described above
** ModelFolder — Described above
** ScenarioOutputFolder — file path identifying the location on the computer hard disk where the built scenarios will be located

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ve.run()
VEScneario_test <- openModel("VEScenario")
VEScneario_test $run()
```
